Embedding Dimension of Polyhedral Losses

### 2020-01-30 colt-20/embed-dim.tex
Separating definition of orderable from intersection graph and stating equality

\begin{definition}[Intersection graph, orderable]
Given a finite property $\gamma: \simplex \to 2^{\R}$, the \emph{intersection graph} has vertices labeled by $\R$ with an edge $(r,r')$ if $\gamma_r \cap \gamma_{r'} \cap \relint(\simplex) \neq \emptyset$, where $\relint(\simplex)$ equals the set of distributions with full support.
  A finite property $\gamma$ is \emph{orderable} if its intersection graph is a path, i.e. a connected graph where every vertex has either one or two neighbors.
\end{definition}
\jessie{Probably for appendix: compare this definition of orderable to level set intersections on hyperplane definition}
\raf{Actually, it occurred to me that we really should use the original definition, since that's from Lambert, but we can also define the incidence graph and state (proof in appendix) that they are equivalent.}
%\begin{observation}
%  A property $g$ is orderable if and only if the set $g_r \cap g_{r'}$, for $r \neq r'$, is always the intersection of a hyperplane with the simplex.
%\end{observation}

>>>>

\begin{definition}[Orderable]\label{def:orderable-hyperplane}
	A finite property $\gamma:\simplex \to 2^\R$ is \emph{orderable} if there is an enumeration of $\R = \{r_1, \ldots, r_{|\R|}\}$ such that for all $i \leq |\R| - 1$, we have $\gamma_{r_i} \cap \gamma_{r_{i+1}}$ is a hyperplane intersected with $\simplex$.
\end{definition}
This definition follows from~\cite[Theorem 3]{lambert2018elicitation}.

\begin{definition}[Intersection graph]\label{def:intersection-graph}
Given a finite property $\gamma: \simplex \to 2^{\R}$, the \emph{intersection graph} has vertices labeled by $\R$ with an edge $(r,r')$ if $\gamma_r \cap \gamma_{r'} \cap \relint(\simplex) \neq \emptyset$, where $\relint(\simplex)$ equals the set of distributions with full support.
\end{definition}
\begin{proposition}
  A finite property $\gamma$ is \emph{orderable} if and only if its intersection graph is a path, i.e. a connected graph where every vertex has either one or two neighbors.
\end{proposition}
\begin{proof}
  $(\implies)$The intersection graph is constructed by adding an edge for each halfspace, which connects only two nodes.
  If three level sets intersected on $\relint(\simplex)$, then the level boundary for any two would not be a halfspace.
  This yields a path for the intersection graph.

  \bigskip
  $(\impliedby)$ If the intersection graph forms a path, then each level set has at most two neighbors.
  As each path has a source, take the corresponding report to be $r_1$, and proceed in order through the path to enumerate the ordering.
  As the property is well-defined on the simplex, the boundaries of the level sets cannot intersect on $\relint(\simplex)$ without adding an edge.
  Combining this fact with the fact that level sets of finite elicitable properties are convex polytopes (and therefore defined as the intersection of a finite number of halfspaces), the level set boundaries must be hyperplanes intersected with $\simplex$. 
\end{proof}

\jessie{Probably for appendix: compare this definition of orderable to level set intersections on hyperplane definition}
\raf{Actually, it occurred to me that we really should use the original definition, since that's from Lambert, but we can also define the incidence graph and state (proof in appendix) that they are equivalent.}
%\begin{observation}
%  A property $g$ is orderable if and only if the set $g_r \cap g_{r'}$, for $r \neq r'$, is always the intersection of a hyperplane with the simplex.
%\end{observation}
